Can government public communications elicit undue trust? Exploring the interaction between symbols and substantive information in communications

### 2018-07-30 paper2_information and symbols_02.Rmd
Add files via upload

EPM is working to reduce the air-pollution in the Haifa-Bay through:

@@

* **Increasing the supervision of the factories in Haifa-Bay**.
In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways. The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the amount of fines for pollutants.

* **Reduction of smoke emissions from vehicles in Haifa Bay**.
The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area. The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and promotes the operation of a "clean-air area" that restricts the entry of polluting vehicles.

@@

* **Decreasing the supervision of the factories in Haifa-Bay**.
The Ministry is preparing for a change in the method of supervision of the factories. The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the amount of fines. The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.

* **Raising citizens' awareness of the efforts to improve air quality**.
In recent years, the Ministry has taken steps to reduce air pollution in Haifa-Bay, which have been partially successful. The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents. To this end, the ministry has increased its investment in public relations and publicity in this subject.

@@

EPM is working to reduce the amount of waste and increase its recycling through:

@@

* **Packaging recycling - Increased supervision of manufacturers**.
In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, which imposes on manufacturers and importers the responsibility for recycling the packaging. The Ministry will work to increase enforcement by virtue of this act, and will enforce it with regard to additional manufacturers and importers.

* **Reducing the usage of disposable bags**.
In order to reduce the use of disposable plastic bags, the Ministry enforces the Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the chains. The Ministry works to implement the act, and encourages the transition to reusable grocery bags.

@@

* **Packaging recycling - Decreased supervision of manufacturers**.
The Ministry is preparing to a change in the method of supervision of the manufacturers, who are responsible for the recycling of product packaging by virtue of the act The ministry will reduce the number of inspections, rely on manufacturers' self-reports regarding their compliance with the requirements of the act, and reduce the amount of fines. The change is coordinated with members of the industry, which are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.

>>>>

EPM is working to reduce the air-pollution in the Haifa-Bay by:

@@

* **Increasing the supervision of the factories in Haifa-Bay**.
In order to reduce the emissions of pollutants from the factories in the industrial area, the Ministry is working to increase the supervision of the factories in several ways. The ministry will increase the number of inspection visits, expand the use of unannounced inspections, and increase the level of fines for polluters.

* **Reduction of emissions from vehicles in Haifa Bay**.
The Ministry is taking a number of actions to reduce the amount of air-pollution from vehicles in the area. The ministry promotes the installation of particle filters in hundreds of vehicles in the area, and the designation of a "clean-air district" from which polluting vehicles are banned.

@@

* **Decreasing the supervision of factories in Haifa-Bay**.
The Ministry is preparing for a change in the method of supervision of the factories. The ministry will reduce the number of inspection visits and unannounced inspections, rely on factories' self-reports on pollutant emissions, and reduce the level of fines. The change is coordinated with members of the industry, which are committed to reducing the pollution, and it will assist to build mutual respect between them and the ministry.

* **Raising citizens' awareness of the efforts to improve air quality**.
In recent years, the Ministry has taken steps to reduce air pollution in Haifa-Bay, which have been partially successful. The Ministry is working to raise awareness of its efforts and to emphasize their success in order to improve its image among the residents. To this end, the ministry has increased its investment in public relations and publicity on this subject.

@@

EPM is working to reduce the amount of waste and increase recycling through:

@@

* **Packaging recycling - Increased supervision of manufacturers**.
In order to reduce the amount of waste generated from packaging and to encourage recycling, the Ministry implements the Packaging act, under which manufacturers and importers are responsible for recycling their packaging materials. The Ministry will work to increase enforcement by virtue of this act, and will enforce it for additional manufacturers and importers.

* **Reducing the usage of disposable bags**.
In order to reduce the use of disposable plastic bags, the Ministry has enforced the Carrier Bags act, which sets a compulsory charge on bags sold in large retail chains and imposes reporting obligations on the retail chains themselves. The Ministry is working to implement the act, and to encourage the transition to reusable grocery bags.

@@

* **Packaging recycling - Decreased supervision of manufacturers**.
The Ministry is preparing to a change in the way manufacturers, who are responsible for the recycling of product packaging, are supervised. The ministry will reduce the number of inspections, rely on manufacturers' own reporting regarding their compliance with the requirements of the act, and will reduce the level of fines. The change is coordinated with industry representatives, who are committed to the issue, and it will assist to strengthen mutual respect between them and the ministry.
